\LARGE \bf Explicit Knowledge and the Deliberative Layer: Lessons Learned

### 2013-03-22 paper.tex
spell checking

This article presents our design choices, the articulations between the diverse
deliberative components of the robot, and the strenghts and weaknesses of this
approach. We show that explicit knowledge management is not only a convenient
tool from the software engineering point of view, but also pushes for a
different, more \emph{semantic} way to address the decision-making issue in
autonomous robots.

@@

Besides, even knowledge that belongs the \emph{common knowledge} may not be
appropriate in a given interaction context. For instance, the system may
compute that at a given instant the human is looking at the object: \stmt{human
looksAt obj1}. This property makes sense to both parties, but in the context of
the \emph{spygame}, we would like to mainly use immanent properties, not
volatile like a gaze. More research is required to indentify relevant
interaction contexts and knowledge classes attached to them.

@@

Since these statements are anchored in the robot's pool of knowledge, they
actually convey shared and unambiguous \emph{meaning} through the system. This
has one important consequence from the perspective of the system architecture:
modules interfaces are only defined in term of knowledge consumption and/or
production. This brings good decoupling properties. For instance, the output of
the dialog module is a new \emph{situation desired} by the speaker. This module
can be transparently replaced or completed by any other module that produces
the same chuncks of knowledge. Only a thin protocol layer remains to get the
modules to interact together. This allows us to implement (otherwise difficult)
merging of radically different perception modalities like vision (the robot
sees an object on a table: the output would look like \stmt{obj1 isOn table1})
and verbal description (a human says to the robot the object on the table
is red: it leads to a query \stmt{? isOn table1} and then a new assertion:
\stmt{obj1 hasColor red}).

Another consequence is that the communication channels are {\it
defacto} defined by the semantics of the information they
convey. This allows the system designers to think in term of which module
produces or needs which knowledge, instead of which module produces which
service. We found this approach to be very helpful when implementing cognitive
functions like the theory of mind, the perspective taking or the natural
language grounding.

@@

\subsubsection{The Cognician view: palpable knowledge and semantic thinking}

>>>>

This article presents our design choices, the articulations between the diverse
deliberative components of the robot, and the strengths and weaknesses of this
approach. We show that explicit knowledge management is not only a convenient
tool from the software engineering point of view, but also pushes for a
different, more \emph{semantic} way to address the decision-making issue in
autonomous robots.

@@

Besides, even knowledge that belongs the \emph{common knowledge} may not be
appropriate in a given interaction context. For instance, the system may
compute that at a given instant the human is looking at the object: \stmt{human
looksAt obj1}. This property makes sense to both parties, but in the context of
the \emph{spygame}, we would like to mainly use immanent properties, not
volatile like a gaze. More research is required to identify relevant
interaction contexts and knowledge classes attached to them.

@@

Since these statements are anchored in the robot's pool of knowledge, they
actually convey shared and unambiguous \emph{meaning} through the system. This
has one important consequence from the perspective of the system architecture:
modules interfaces are only defined in term of knowledge consumption and/or
production. This brings good decoupling properties. For instance, the output of
the dialog module is a new \emph{situation desired} by the speaker. This module
can be transparently replaced or completed by any other module that produces
the same chunks of knowledge. Only a thin protocol layer remains to get the
modules to interact together. This allows us to implement (otherwise difficult)
merging of radically different perception modalities like vision (the robot
sees an object on a table: the output would look like \stmt{obj1 isOn table1})
and verbal description (a human says to the robot the object on the table
is red: it leads to a query \stmt{? isOn table1} and then a new assertion:
\stmt{obj1 hasColor red}).

Another consequence is that the communication channels are {\it
de facto} defined by the semantics of the information they
convey. This allows the system designers to think in term of which module
produces or needs which knowledge, instead of which module produces which
service. We found this approach to be very helpful when implementing cognitive
functions like the theory of mind, the perspective taking or the natural
language grounding.

@@

\subsubsection{The Cognitician view: palpable knowledge and semantic thinking}
